%------------------------
% Resume Template
% Author : Aryan odugoudar
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Joshita Das}} & Email: \href{mailto:}{joshita.das2021@vitstudent.ac.}\\
   Mobile:~~~+91-9665149164 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Chennai, India}
      {Bachelor of Technology - Computer Science Engineering ;  GPA: 8.43}{August 2021 - June 2025}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Networking, Databases, Robotics, IoT, Sensors and Actuators}}}
    \resumeSubHeadingListEnd
	    
\vspace{-2pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~C++, Haskell, Python, C, SQL, JAVA}
	\resumeSubItem{Frameworks}{~~~~Scikit, TensorFlow, Keras, Selenium}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~ GIT, MySQL, SQLite, Sphinx, LaTeX, Matlab, ThingsBoard, HiveMQ, Anaconda, Node-RED, Supervisor}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Web, Windows, Arduino, Raspberry, AWS, Azure}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Program Management, Writing, Public Speaking, Critical Thinker}

\resumeSubHeadingListEnd
\vspace{-2pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
		{ServiceNow}{Hyderabad}
		{Associate Software Quality Engineer}{June 2024 -  August 2024}
		\resumeItemListStart
        \resumeItem{Developed and executed automated test scripts using Selenium to streamline backlog items on the company’s main web page.}
          {Identified and documented bugs, performance issues, and enhancements, contributing to the overall improvement of the web application.}
        \resumeItem{Impact}{In progress.}
    \resumeItemListEnd
\vspace{-2pt}
    \resumeSubheading{Corporate Gurukul}{Singapore}
    {Teaching Assistant}{December 2023}
    \resumeItemListStart
        \resumeItem{Artificial Intelligence for Young Achievers}
          {Managed over 40 students at the National University of Singapore.}
          \resumeItem{Collaborated with NUS professors and AWS professionals}
          { Facilitated lectures, grade assignments, and conduct doubt-clearing sessions, ensuring a vibrant and supportive learning environment.}
          \resumeItem{Management and Logistics}{ Worked closely with faculty and teaching staff to ensure a seamless program delivery, fostering an enriching educational experience.}
      \resumeItemListEnd
\vspace{-2pt}
    \resumeSubheading
		{TalenSprint }{Hybrid}
		{Software Intern}{May 2023 -  July 2023}
		\resumeItemListStart
        \resumeItem{Dashboard to visualize background Linux scripts}
          {Enabled a dashboard by the Supervisor software to help operations department visualize the scripts.}
        \resumeItem{Optimization and Customization of Supervisorctl}{Documented and analyzed the inbuilt code for Supervisor web and modified the program to help the company receive desired results}
		\resumeItemListEnd
\vspace{-2pt}
    \resumeSubheading
		{National University of Singapore \& HPE }{On-Site}
		{Academic Intern}{June 2022 -  July 2022}
		\resumeItemListStart
        \resumeItem{Deep Learning solution to analyze Autism}
          {Developed a Deep learning solution to identify Autism based on Image Classification with an accuracy of 88\%.}
        \resumeItem{Deep Learning and Data Analytics}{Programmed VGG-19 and Exception models to understand the involvement of facial features in detecting Autism.}
		\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\vspace{-2pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Glass and plastic detecting dustbin (Computer vision, ROS, C, IOT)}{An IOT solution which segregates plastic and glass. It also alerts once it is over filled(March '24)}
\vspace{2pt}
\resumeSubItem{Continual Learning-based Malware Detection System (Continual Learning, NLP)}{Model to detect new malware 60\% more effectively by comparing Class IL, Task IL and domain IL. Tech: Python, Anaconda\& OpenCV. (August '22)}
\vspace{2pt}
\resumeSubItem{Object detecting micro-car (Ultrasonic Sensors, Arduino UNO, Motors)}{Detecting 
obstacles robot making decisions based on the sensor data. Accuracy of the robot being 98\% .(May '23)}
\vspace{2pt}
\resumeSubItem{Building Neural Network using Napkin Mathematics (Machine Learning \& mathematics)}{Built and Programmed in Python a perceptron, sigmoid and various layers from scratch to understand and research the underlying mathematics. (Feb '24)}
\vspace{2pt}
\resumeSubItem{Product Demand Analysis(Machine Learning \& Natural Language Processing)}{Using Machine Learning models to predict the drop in prices in products by analyzing customer behaviours which will help reduce loss by 40 \%. ( On-going)}
\resumeSubHeadingListEnd
\vspace{-2pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\resumeSubItem {Intel Unnathi Hackathon Finalist}{ One of the top 10 teams selected from over 500 eligible teams across the country.
Contributed positively is the data analysis of the traffic alerts collected by IIIT Hyderabad and created a project using IDD.}
\vspace{-2pt}
\resumeSubItem {Women Engineers' Scholar supported by Google (June 2022)}{ One of the 250 scholars selected from over 30,000 eligible applicants across the country.
Courses: Linux, Haskell, Set-theory, Golang, Machine Learning}
\vspace{-2pt}
\resumeSubItem{Honeywell Leadership Challenge Academy Ambassador (September 2022) }{One of the 2 students selected from thousands of applicants ranging from 60 countries to represent Honeywell in the US SPACE AND ROCKET CENTRE and guide 300 students to understand STEM concepts.}
\end{description}
\vspace{-5pt}
\resumeSubHeadingListEnd

\end{document}